A coupled particle level set and Moment-of-fluid method for simulating multiphase flows with phase change \thanks{this material is based upon work supported by National Aeronautics and Space Administration under grant number 80NSSC20K0352}

### 2024-03-12 main.tex
main.tex

ABSTRACT:
An improved algorithm for computing multiphase flows is presented in 
which the multimaterial Moment-Of-Fluid (MOF) algorithm for multiphase flows, 
described by Li et al (2015), is enhanced with 
meshless particles.  The new method is less ``dissipative'' than the 
Continuous Moment of Fluid method (``CMOF,'' Ye at el (2023)) and inherently 
removes the ``checkerboard instability'' that persists when using the 
MOF method on surface tension driven multiphase (multimaterial) 
flows (Li et al (2015)).

Multiphase flow examples are shown in 2D, 3D axisymmetric ``RZ,'' and 
3D coordinate systems.  Examples include two material and three 
material multiphase flows: bubble formation, the impingement of a 
liquid jet on a gas bubble in a cryogenic fuel tank, freezing, melting,
evaporation, and liquid lens dynamics.
%%compare with Vu SI.
% Fred Stern -> reconstructed distance function coupled with VOF 
%%cite: Mukundan
\linenumbers
\section{Introduction}
In Ye et al\cite{YeEstebe...},
an improved ``Continuous Moment-of-Fluid'' (CMOF) algorithm
for computing solutions to multiphase (multimaterial) flows was
presented for overcoming the interface curvature ``checkerboard'' problem
present in the ``Moment of Fluid'' (MOF) \cite{MOF}  method.  
Also in Ye et al\cite{YeEstebe...}, a novel decision tree data science 
approach was presented for accelerating the CMOF slope reconstruction 
algorithm.

In this article, we present a ``Particle Level Set Moment-of-Fluid''
method for overcoming the interface checkerboard prolem.  This new approach
we claim is more accurate and faster than the CMOF approach and 
does not require the expensive initial training step.  We also claim that
our new approach is faster and more accurate than the CLSVOF 
method\cite{SusPuckett} with the added capability for simulating
general multimaterial (>2 materials) mutiphase flows.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.4\textwidth]{checkerboardMOF.eps}
\includegraphics[width=0.4\textwidth]{checkerboardCMOF.eps}
%%REMMERSWAAL and Veldman's parabolic reconstruction WILL NOT SEE
%%the checkerboard pattern (even though they take both F and x into
%%account).
\caption{LEFT:
 Standard curvature discretization methods 
 \cite{sussman2003second,cummins2005estimating,REMMERSWAAL2022111473}
 will predict zero curvature for this saw-tooth
 interface since the volume fractions {\em and} 
 centroids vary only
 in the $y$ direction.  Repeated Moment-of-Fluid (MOF)
 (i) reconstruction followed by (ii) the replacement of the reference
 centroid with the MOF actual centroid will not alter the initial interface
 (ignoring round-off error).  RIGHT: the gaps in the initial saw-tooth 
 interface are reduced by at least a factor of 3 after a single replacement
 of the reference centroid with the CMOF actual centroid.
 \label{checkerboard} }
\end{figure}

>>>>

ABSTRACT:
An improved algorithm for computing multiphase flows is presented in 
which the multimaterial Moment-Of-Fluid (MOF) algorithm for multiphase flows, 
described by Li et al (2015), is enhanced with 
meshless particles.  The new method is less ``dissipative'' than the 
Continuous Moment of Fluid method (``CMOF,'' Ye at el (2023)) and inherently 
removes the ``checkerboard instability'' that is present when using the 
MOF method on surface tension driven multiphase (multimaterial) 
flows (Li et al (2015)).

Multiphase flow examples are shown in 2D, 3D axisymmetric ``RZ,'' and 
3D coordinate systems.  Examples include two material and three 
material multiphase flows: bubble formation, the impingement of a 
liquid jet on a gas bubble in a cryogenic fuel tank, freezing, melting,
evaporation, and liquid lens dynamics.
%%compare with Vu SI.
% Fred Stern -> reconstructed distance function coupled with VOF 
%%cite: Mukundan
%%compare MOF to CMOF to PLSMOF for static freezing test.
\linenumbers
\section{Introduction}
In Ye et al\cite{YeEstebe...},
an improved ``Continuous Moment-of-Fluid'' (CMOF) algorithm
for computing solutions to multiphase (multimaterial) flows was
presented for overcoming the interface curvature ``checkerboard'' problem
present in the ``Moment of Fluid'' (MOF) \cite{MOF} method.  
Also in Ye et al\cite{YeEstebe...}, a novel decision tree data science 
approach was presented for accelerating the CMOF slope reconstruction 
algorithm.

In this article, we present a ``Particle Level Set Moment-of-Fluid'' (PLSMOF)
method for overcoming the interface checkerboard prolem.  This new approach
we claim is more accurate and faster than the CMOF approach and 
does not require the expensive initial training step.  We also claim that
our new approach is faster and more accurate than the CLSVOF 
method\cite{SusPuckett} with the added capability for simulating
general multimaterial (>2 materials) mutiphase flows.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.4\textwidth]{checkerboardMOF.eps}
\includegraphics[width=0.4\textwidth]{checkerboardPLSMOF.eps}
%%\includegraphics[width=0.4\textwidth]{checkerboardCMOF.eps}
%%REMMERSWAAL and Veldman's parabolic reconstruction WILL NOT SEE
%%the checkerboard pattern (even though they take both F and x into
%%account).
\caption{LEFT:
 Standard curvature discretization methods 
 \cite{sussman2003second,cummins2005estimating,REMMERSWAAL2022111473}
 will predict zero curvature for this saw-tooth
 interface since the volume fractions {\em and} 
 centroids vary only
 in the $y$ direction.  Repeated Moment-of-Fluid (MOF)
 (i) reconstruction followed by (ii) the replacement of the reference
 centroid with the MOF actual centroid will not alter the initial interface
 (ignoring round-off error).  RIGHT: the gaps in the initial saw-tooth 
 interface are immediately removed with PLSMOF reconstruction since the
 level set function is derived as the exact signed distance function to the
 initial MOF reconstructed interface, and the particles are initialized from
 the level set function.  Ensuing slopes
 are derived from a combination of the particles and the signed
 distance function (if particles available).
 \label{checkerboard} }
\end{figure}
